---
title: "lAddPats Module Vignette"
output: 
  rmarkdown::html_document:
      toc: true
      toc_float: true
      toc_depth: 3
      fig_caption: yes
      highlight: textmate
vignette: >
  %\VignetteIndexEntry{lAddPats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 6, fig.width = 7)

source("..\\R\\lAddPats.R")

```

# Introduction

This vignette aims to describe the helper module *lAddPats* of the *simple* package.
The purpose of the module is to control the technical process of adding newly simulated patients to the respective ISA datasets.

## Function arguments

The module will take the current platform trial status at time **t**, as well as arguments specific to this task as input parameters.

#### Current status of platform trial `lPltfTrial` 

This is a snapshot image of the current platform trial status and changes during the simulation. The current time or number of active arms could be examples of variables of interest which we would like to access.

#### Additional arguments `lAddArgs`

Apart from the trial snapshot, module specific variables can be added. 


## Functions

### Constructor Function
The idea is to be able to include the platform snapshot as well as any additionally relevant variables outside the simulation.

The central function of the module is `new_lAddPats`. It defines the technical process of adding newly simulated patients to the ISA datasets.

```{r}
new_lAddPats()
```

**`$fnAddPats`**
The necessary input is a function `fnAddPats` determining how (from a technical perspective) newly simulated patient data is added to the existing ISA datasets.
Within the curly braces `{}` you execute the function operations.

**`$lAddArgs`**
Here you can supply the list with additional arguments, which are accessed in the function above.


### Helper function

It is recommended to use the helper function `lAddPats`. By default, the newly simulated patients are going to be copied from their temporary location within `lSnap` into the respective ISA datasets.
```{r}
lAddPats
```


### Summary

The summary call provides information about the input you provided. It gives an overview about snapshot and additional variables as well the function that was implemented.

```{r}
summary(lAddPats())
```


# Final remarks

It is recommended to use the default function.
