---
title: "lAddIntr Module Vignette"
output: 
  rmarkdown::html_document:
      toc: true
      toc_float: true
      toc_depth: 3
      fig_caption: yes
      highlight: textmate
vignette: >
  %\VignetteIndexEntry{lAddIntr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 6, fig.width = 7)

source("..\\R\\lAddIntr.R")

```

# Introduction

This vignette aims to describe the helper module *lAddIntr* of the *simple* package.
The purpose of the module is to control the technical process of creating a copy of the interventions design blueprints stored in `lPltfDsgn` in the actual platform trial `lPltfTrial`.

## Function arguments

As input variables to determine which intervention blueprint to use, the module will take the platform design list, platform trial status at time **t**, as well as arguments specific to this task.

#### Platform trial design list `lPltfDsgn` 

This is the comprehensive list of platform design options specified, including the sub-list `lIntrDsgn`, where the interventions design blueprints are stored.

#### Current status of platform trial `lPltfTrial` 

This is a snapshot image of the current platform trial status and changes during the simulation. The current time or number of active arms could be examples of variables of interest which we would like to access.

#### Additional arguments `lAddArgs`

Apart from the trial snapshot, module specific variables can be added. In the case of this module, the `nTrt` variable has two meanings and is essential for this module to work correctly: 1) In the beginning of the trial, the number `nTrt` gives the number of ISAs that will start in the trial. 2) At later stages, the number `nTrt` will be overwritten by the actual simulation and let this module know, how many ISAs enter at a particular point in time.


## Functions

### Constructor Function
The idea is to be able to include the platform snapshot as well as any additional variable you would want to impact your recruitment.

The central function of the module is `new_lAddIntr`. It defines the technical process of entering a new intervention into the ongoing trial.

```{r}
new_lAddIntr()
```

**`$fnAddIntr`**
The necessary input is a function `fnAddIntr` determining how interventions are included from the blueprints found in `lPltfDsgn`. In the function call you further input the current platform trial status to be used in the `lPltfTrial` argument and determine the list with further arguments which affect this task in `lAddArgs`. 
Within the curly braces `{}` you execute the function operations.

**`$lAddArgs`**
Here you can supply the list with additional arguments, which are accessed in the function above. It is essential to have an `nTrt` variable (see above).


### Helper function

It is recommended to use the helper function `lAddIntr`. By default, the next unused intervention in the list of intervention blueprints `lIntrDsgn` within `lPltfDsgn` will be included.
```{r}
lAddIntr
```

The only argument you have to enter is the number of interventions starting in the beginning of the trial. 


### Summary

The summary call provides information about the input you provided. It gives an overview about snapshot and additional variables as well the function that was implemented.

```{r}
summary(lAddIntr(2))
```


# Final remarks

In the vanilla version of *simple*, each intervention design in `lIntrDsgn` can only be used once.
