---
title: "Intervention Inclusion Module Vignette"
output: 
  rmarkdown::html_document:
      toc: true
      toc_float: true
      toc_depth: 3
      fig_caption: yes
      highlight: textmate
vignette: >
  %\VignetteIndexEntry{Intervention Inclusion Module Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
  

---
```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 4, fig.width = 7)

source("..\\R\\lNewIntr.R")
```


## Introduction

This vignette aims to describe the intervention inclusion module *lNewIntr* of the *simple* package.
The purpose of the module is to control the inclusion and exclusion of ISA's over time. 

## Function arguments

As input variables to determine the patient accrual at time **t**, the module will take the platform trial status at time **t**, as well as arguments specific to the intervention inclusion.

#### Current status of platform trial `lPltfTrial` 

This is a snapshot image of the current platform trial status and changes during the simulation. The current time or number of active arms could be examples of variables of interest which we would like to access.
 

#### Additional arguments `lAddArgs`

Apart from global variables, module specific variables can be added. Examples which are later implemented in the *Examples* section are:

* Different probability parameters *prob* for different points in time.
* A maximum number of total interventions to be included in the trial *nIntrMax*.
* A fixed waiting period *nTimeDiff* after which a new intervention is added

## Functions

### Constructor Function `new_lNewIntr`
The idea is to be able to include snapshot variables of the simulation as well as any additional variable you would want to impact your recruitment.

The central function of the module is `new_lNewIntr`. It defines the "rules" of intervention inclusion you want to implement in the simulation.

```{r}
new_lNewIntr()
```

**`$fnNewIntr`**
The necessary input is a function `fnNewIntr` determining when new interventions are added. In the function call you input the snapshot variables to be used in the `lPltfTrial` argument and determine the list with further arguments which affect your algorithm in `lAddArgs`. 
Within the curly braces `{}` you execute the function operations.

**`$lAddArgs`**
Here you can supply the list with additional arguments, which are accessed in the function above.


### Helper function `lNewIntr`

If you do not want to think about an inclusion strategy for interventions, you can use the helper function `lNewIntr`. 
```{r}
lNewIntr
```

The only argument you have to enter is the maximum number of total arms you want to allow for the trial. The function then adds an intervention whenever an ISA leaves until the maximum number is reached.
For example: 

```{r}
x <- lNewIntr(5)
```



### Plot

Plotting objects created by `lNewIntr` or `new_lNewIntr` displays the number of active and finished interventions over time.

There are a few global variables that this specific plot function requires. `dCurrTime` states the current time point and needs to start with 1. `cIntrTime` and `dIntrTimeParam` describe the in-trial-time of interventions. Depending on the input for `cIntrTime` the function expects different types of input for `dIntrTimeParam`:

* `cIntrTime` = "fixed"
  + `dIntrTimeParam` $\in \mathbb{N}$ 
  + natural number determining how many time units interventions stay in the trial
* cIntrTime` = "random"
  + `dIntrTimeParam` $\in (0,1)$
  + probability of an ISA leaving the trial at every time step


By default ISA's leave after 10 time units which means that `cIntrTime` is "fixed" with `dIntrTimeParam` 10.

For the actual plot you just call `plot()` with the object you want to plot.

```{r}
x <- lNewIntr(5)
plot(x)
```

Any changes in global variables can be specified in the plot call. If you are only interested in 20 time steps rather than 52 and want trials to leave with a probability of 0.2 every time step you can call:

```{r}
x <- lNewIntr(10)
plot(
  x,
  dCurrTime = 1:20,
  cIntrTime = "random",
  dIntrTimeParam = 0.2
)
```


Optionally you can also state the global variables you added in the object created by the `new_lRecrPars` function.


### Summary

The summary call provides information about the input you provided. It gives an overview about snapshot and additional variables as well the function that was implemented.

```{r}
summary(x)
```


## Examples

1. **Replace outgoing ISAs with helper function**

```{r}

x <- lNewIntr(4)
# in default version, replace every outgoing ISA until a maximum number of ISAs (in this case 4)
plot(x)
# default plot assumes an in-trial time for ISAs of 10 time steps
summary(x)

```

***

2. **Add an intervention every 4 time units**


```{r}

x <- 
  new_lNewIntr(
    fnNewIntr  = function(lPltfTrial, lAddArgs) {
      # if it has been 4 time units since last inclusion, add one ISA
      if (lPltfTrial$lSnap$dCurrTime == max(lPltfTrial$lSnap$vIntrInclTimes) + lAddArgs$nTimeDiff) {
        dAdd <- 1
      } else {
        dAdd <- 0
      }
      return(dAdd)
    },
    lAddArgs      = list(nTimeDiff = 4)
  )
plot(x)
summary(x)

```

***

3. **Random entry of ISAs, add max 2 at a time, maximum 5 parallel**
```{r}

# Add ISAs with random probability
# never more than two at the same time and never allow more than 5 to run in parallel

x <- 
  new_lNewIntr(
    fnNewIntr  = function(lPltfTrial, lAddArgs) {
      
      if (lPltfTrial$lSnap$dActvIntr < lAddArgs$nIntrMax) {
        dAdd <- min(rbinom(1, 3, lAddArgs$prob_inclusion), lAddArgs$nIntrMax - lPltfTrial$lSnap$dActvIntr)
      } else {
        dAdd <- 0
      }
      return(min(2, dAdd))
    },
    lAddArgs      = list(
      nIntrMax = 5,
      prob_inclusion = 0.4
    )
  )
plot(x)
summary(x)


```

***

4. **As before, with inclusion stop for some time points**

```{r}

x <- 
  new_lNewIntr(
    fnNewIntr  = function(lPltfTrial, lAddArgs) {

      if (lPltfTrial$lSnap$dActvIntr < lAddArgs$nIntrMax & lPltfTrial$lSnap$bInclAllowed) {
        dAdd <- min(rbinom(1, 3, lAddArgs$prob_inclusion), lAddArgs$nIntrMax - lPltfTrial$lSnap$dActvIntr)
      } else {
        dAdd <- 0
      }
      return(min(2, dAdd))
    },
    lAddArgs      = list(
      nIntrMax = 5,
      prob_inclusion = 0.4
    )
  )
plot(
  x,
  bInclAllowed = c(
    rep(TRUE, 15), 
    rep(FALSE, 15), 
    rep(TRUE, 22)
  )
)
summary(x)

```

***

5. **Different probabilities of inclusion for different time points**

```{r}

# Every 7th time step the probability for inclusion of an arm is increased
x <- new_lNewIntr(
  fnNewIntr = function(lPltfTrial, lAddArgs) {
    if(lPltfTrial$lSnap$dCurrTime %% 7 == 0){
      dAdd <- sample(c(1,0), 1, prob = c(lAddArgs$prob_incl_1, 1-lAddArgs$prob_incl_1))
    } else {
      dAdd <- sample(c(1,0), 1, prob = c(lAddArgs$prob_incl_2, 1-lAddArgs$prob_incl_2))
    }
    return(dAdd)
  },
  
  lAddArgs = list(prob_incl_1 = 0.8, prob_incl_2 = 0.1)
)

plot(x)


```

***

6. **Random end of ISAs**
```{r}

# Now the end of ISAs is not after a fixed interval but is randomly drawn
# On average every 5 days an arm enters, and every 10 days an arm leaves

x <- new_lNewIntr(
  fnNewIntr = function(lPltfTrial, lAddArgs) {
    dAdd <- sample(c(1,0), 1, prob = c(lAddArgs$prob_incl, 1-lAddArgs$prob_incl))
    
    return(dAdd)
  },
  lAddArgs = list(prob_incl = 0.2)
)

plot(
  x,
  cIntrTime = "random",
  dIntrTimeParam = 0.1
)


```


# Exercises

Below will be some tasks of increasing complexity to make you comfortable using the module and figure out difficulties.

## Tasks

Try to use the module to program the following tasks according to the instructions. The solutions are given below. The examples of the vignette may serve as a helping hand. The plots below show what the plotted output could look like.


**1. With a 50:50 % chance let 1 or 2 ISAs enter every 5th time unit and let the maximum number of total ISAs be 10.**

```{r}
x <- new_lNewIntr(
  fnNewIntr = function(lPltfTrial, lAddArgs){
    
    # if the conditions are met (every 5th time unit & there are less than 10 ISAs so far) we randomly draw 1 or 2 to determine how many ISAs should be added
    if((lPltfTrial$lSnap$dCurrTime %% 5 == 0) & (length(lPltfTrial$lSnap$vIntrInclTimes) < lAddArgs$nIntrMax)){
      dAdd <- sample(c(1,2), 1)
    } else {
      
      # otherwise no ISA is added
      dAdd <- 0
    }
      
  },
  
  # here we set the maximum number of total interventions to 10
  lAddArgs = list(nIntrMax = 10)
)

plot(x)
```



**2. Let the entry of ISAs be random, with an entry probability of 0.2 at each time step, the maximum number of total ISAs be 6 and the maximum number of parallel ISAs be 3. For visualization, let the ISAs duration be 12.**

*Hint: duration of ISAs is specified in the plot function, as this is not a feature of the lNewIntr module.


```{r}

x <- new_lNewIntr(
  fnNewIntr = function(lPltfTrial, lAddArgs){
    # if the conditions are met (number of parallel ISAs <3, number of total ISAs < 6) we randomly draw if an ISA is added with the stated probabilities
    if((length(lPltfTrial$lSnap$IntrInclTimes) < lAddArgs$nIntrMax) & (lPltfTrial$lSnap$dActvIntr < lAddArgs$nIntrParallel)){
      dAdd <- sample(c(1,0), 1, prob = c(lAddArgs$prob, 1-lAddArgs$prob))
    } else {
      dAdd <- 0
    }
    
    return(dAdd)
  },
  
  # here the additional arguments are specified (max number of parallel interventions, max number of total interventions, entry probability)
  lAddArgs = list(
    nIntrParallel = 3,
    nIntrMax = 6,
    prob = 0.2
  )
)


# here we set the duration of interventions to be fixed (intr_itt) with duration 12 (intr_itt_param)
plot(
  x,
  cIntrTime = "fixed",
  dIntrTimeParam = 12
)

```

**3. Let the entry and exit of ISAs be random with probabilities 0.2 and 0.1 respectively. Only consider a simulation period of 40 timesteps instead of the default of 52. Additionally no recruitment should happen between time unit 10 and 20.**

*Hint: the number of time steps, recruitment window and exit probability are specified in the plot function, as these are not features of the lNewIntr module.


```{r}
x <- new_lNewIntr(
  
  fnNewIntr = function(lPltfTrial, lAddArgs){
    if(lPltfTrial$lSnap$bInclAllowed){
      dAdd <- sample(c(1,0), 1, prob = c(lAddArgs$prob, 1-lAddArgs$prob))
    } else {
      dAdd <- 0
    }
      return(dAdd)
    },
  
  lAddArgs = list(prob = 0.2)
  
)

# here we set the arguments which are not part of the lNewIntr module, but are still specified
# we have to state that the exit of ISAs is random (intr_itt) with a probability of 0.1 (intr_itt_param) at each time step. Additionally we change the simulation duration (dCurrTime) to 40 time steps and define the enrollment window (bInclAllowed).
plot(
  x,
  cIntrTime = "random",
  dIntrTimeParam = 0.1,
  dCurrTime = 1:40,
  bInclAllowed = c(rep(TRUE, 10), rep(FALSE, 10), rep(TRUE, 20)), # has to be a vector of the same length as dCurrTime so that for each time step a value can be taken from the vector
)
```



### Remarks

The snapshot variables saved in the list *lPltfTrial* have a fixed name which should not be changed as it is implemented in many different modules. As mentioned above the vignette of the module *lPltfTrial* will contain an overview of all the snapshot variables used in any module.
