---
title: "Recruitment Parameters Module Vignette"
output: 
  rmarkdown::html_vignette:
      toc: true
      toc_depth: 3
      fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Recruitment Parameters Module Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
  

---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 6, fig.width = 7)

source("..\\R\\lRecrPars.R")

```

## Introduction

This vignette aims to describe the recruitment module of the *simple* package.
The purpose of the module is to control the recruitment of patients over time. 

## Function arguments

The module will have global variables as well as specific arguments that can be added and specified in the recruitment function

#### Global variables `lGlobVars` 

Global variables are inputs that are used in different modules and change during the simulation. The current time could be an example for a variable of interest for which it makes sense to be globally available.

#### Additional arguments `lAddArgs`

Apart from global variables, module specific variables can be added. Examples which are later implemented in the *Examples* section are:

* different distribution parameters *lambda* for different points in time.
* a *cap* if you want to have a maximum number of patients to be recruited per time step.
* an enrollment window, if you want to prohibit recruitment for some periods.

## Functions

### Constructor Function
The idea is to be able to include global variables of the simulation as well as any additional variable you would want to impact your recruitment.

The central function of the module is `new_lRecrPars`. It defines the "rules" of recruitment you want to implement in the simulation.

```{r}
new_lRecrPars()
```

**`$fnRecrProc`**
The necessary input is a function `fnRecrProc` determining how patients are recruited over time. In the function call you input the global variables to be used in the `lGlobVars` argument and determine the list with further arguments which affect your recruitment algorithm in `lAddArgs`. 
Within the curly braces `{}` you execute the function operations.

**`$lAddArgs`**
Here you can supply the list with additional arguments, which are accessed in the function above.


### Helper function

If you do not want to think about a recruitment strategy, you can use the helper function `lRecrPars`. 
```{r}
lRecrPars
```

The only argument you have to enter is the average number of patients added per time step. The function then draws from a poisson distribution.
For example `lRecrPars(10)` gives the following output when plotted:

```{r}
x <- lRecrPars(10)
plot(x)
```



### Plot

Plotting objects created by `lRecrPars` or `new_lRecrPars` displays the development of patients recruitment as well as the number of active arms over time.

Global variables that this specific plot function requires are `dCurrTime` and `dActvIntr`, describing the current time and the number of active arms at the current time respectively. By default the current time goes from 1 to 52 and only one arm is active at every time point. These vectors have to be of the same length.

For the actual plot you just call `plot()` with the object you want to plot.

```{r}
x <- lRecrPars(10)
plot(x)
```

Any changes in global variables can be specified in the plot call. If you are only interested in 20 time steps rather than 52 and want to have more than one active arm for some time steps you can call:

```{r}
x <- lRecrPars(10)
plot(x,
     dCurrTime = 1:20,
     dActvIntr = c(rep(1,10),
                   rep(2,10)))
```


Optionally you can also state the global variables you added in the object created by the `new_lRecrPars` function.



### Summary

The summary call provides information about the input you provided. It gives an overview about global and additional variables as well the function that was implemented.

```{r}
summary(x)
```


## Examples

1. **Poisson distributed recruitment**

The easiest way is to simply use:

```{r}
x <- lRecrPars(10)

plot(x)
summary(x)
```

***

2. **Decreasing enrollment over time**

```{r}
#every time step draw from poisson distribution with lambda = 50 / current time
x <- new_lRecrPars(
  fnRecrProc = function(lGlobVars, lAddArgs) {
    rpois(1, 50 / lGlobVars$lVars$dCurrTime)
  }
)

plot(x)
summary(x)

```

***


3. **Enrollment where every 7th time unit more patients enter**


```{r}

x <- 
  new_lRecrPars(
    fnRecrProc = function(lGlobVars, lAddArgs) {
      if(lGlobVars$lVars$dCurrTime %% 7 == 0) {
        rpois(1, lambda = lAddArgs$lambda2)
      } else {
        rpois(1, lambda = lAddArgs$lambda1)
        }
      },
    lAddArgs   = list(lambda1 = 2, lambda2 = 20)
  )
plot(x)
summary(x)
```

***

4. **Exponential enrollment with different number of open active arms that is capped**

```{r}
x <- 
  new_lRecrPars(
    fnRecrProc = function(lGlobVars, lAddArgs) {
        min(lAddArgs$growth ^ lGlobVars$lVars$dCurrTime * lGlobVars$lVars$dActvIntr, lAddArgs$cap)
    },
    lAddArgs   = list(growth = 1.2, cap = 100)
  )

# Only simulate 30 time steps
plot(
  x, 
  dCurrTime = 1:30, 
  dActvIntr = c(rep(1, 10),
                rep(2, 10),
                rep(1, 10))
)
summary(x)

```

***

5. **Recruitment depends on global variable that enables recruitment only during a certain time window and additionally makes the number of patients enrolled dependent on the number of active arms**

```{r}
x <- 
  new_lRecrPars(
    fnRecrProc = function(lGlobVars, lAddArgs) {
      pat <- rpois(1, lambda = lAddArgs$lambda) * lGlobVars$lVars$dActvIntr * 6
      ifelse(lGlobVars$lVars$bEnrOpen, pat, 0)
    },
    lAddArgs   = list(lambda = 4)
  )

plot(
  x, 
  dActvIntr = c(
    rep(1, 15), 
    rep(2, 10), 
    rep(3, 10), 
    rep(2, 10), 
    rep(1,7)
  ),
  bEnrOpen = c(
    rep(TRUE, 20),
    rep(FALSE, 10),
    rep(TRUE, 22)
  )
)
summary(x)
```

***

6. **Function using sine of current time**

```{r}
x <- 
  new_lRecrPars(
    fnRecrProc = function(lGlobVars, lAddArgs) {
      100 * (1 + sin(lGlobVars$lVars$dCurrTime))
    }
  )

plot(x)
```

