---
title: "lStopRule Module Vignette"
output: 
  rmarkdown::html_document:
      toc: true
      toc_float: true
      toc_depth: 3
      fig_caption: yes
      highlight: textmate
vignette: >
  %\VignetteIndexEntry{Intervention Inclusion Module Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
  

---
```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height = 4, fig.width = 7)

source("..\\R\\lStopRule.R")
```


## Introduction

This vignette aims to describe the module *lStopRule* of the *simple* package.
The purpose of the module is to control under which conditions the platform trial simulation stops. 

## Function arguments

As input variables to determine whether the platform trial shoudl end at time **t**, the module will take the platform trial status at time **t**, as well as arguments specific to the intervention inclusion.

#### Current status of platform trial `lPltfTrial` 

This is a snapshot image of the current platform trial status and changes during the simulation. The current time or number of ISAs with a final decision could be examples of variables of interest which we would like to access.
 

#### Additional arguments `lAddArgs`

Apart from global variables, module specific variables can be added. 

## Functions

### Constructor Function `new_lStopRule`
The idea is to be able to include the platform snapshot as well as any additionally relevant variables outside the simulation.

The central function of the module is `new_lStopRule`. It defines the "rules" of when to stop the platform trial simulation.

```{r}
new_lStopRule()
```

**`$fnStopRule`**
The necessary input is a function `fnStopRule` checking if the platform trial should be stopped. In the function call you input the snapshot variables to be used in the `lPltfTrial` argument and determine the list with further arguments which affect your algorithm in `lAddArgs`. 
Within the curly braces `{}` you execute the function operations.

**`$lAddArgs`**
Here you can supply the list with additional arguments, which are accessed in the function above.


### Helper function `lStopRule`

If you do not want to think about an inclusion strategy for interventions, you can use the helper function `lStopRule`. 
```{r}
lStopRule
```

There are two default options: Stopping after a certain number of time units (as we mostly think of a week as one time unit, this parameter is called `nWeeks`) or after all ISAs that were entered into the platform have a final decision and therefore no ISA is active anymore (`bNoActive`). 


### Summary

The summary call provides information about the input you provided. It gives an overview about snapshot and additional variables as well the function that was implemented.

```{r}
summary(lStopRule(bNoActive = TRUE))
```


## Examples

1. **Stopping after a certain number of time units**

Stopping after 100 time units:

```{r}

x <- lStopRule(nWeeks = 100)
summary(x)

```

***

2. **Stopping when no ISA is active anymore**


```{r}

x <- lStopRule(bNoActive = TRUE)
summary(x)

```

***

3. **Stop after the first postitive decision has been made for any ISA**

Please note that the way these stopping rules are dependent on how "positive decision" was defined in the `lSynthRes` modules. We assume here (and this is set by default) that a positive decision is coded by a "Efficacy" string in the object `cEndReason` object of the ISAs.

```{r}

# Check if for any ISA a positive decision was made

x <- 
  new_lStopRule(
    fnStopRule  = function(lPltfTrial, lAddArgs) {
      
      ret <- 
        ifelse(
          any(
            sapply(lPltfTrial$isa, function(x) x$cEndReason) == "Efficacy", 
            na.rm = TRUE
            ), 
          1, 
          0
        )
      
      return(ret)
      
    },
    lAddArgs      = list()
  )

```


### Remarks

The snapshot variables saved in the list *lPltfTrial* have a fixed name which should not be changed as it is implemented in many different modules. As mentioned above the vignette of the module *lSnap* will contain an overview of all the snapshot variables used in any module.
