---
title: "Vignette for Authors"
output:
  rmarkdown::html_document:
    toc: true
    toc_float: true
    fig_caption: yes
    highlight: textmate
    code_folding: show
vignette: >
  %\VignetteIndexEntry{VignetteAuthors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(simple)
```

# Purpose

This vignette is intended for authors of the **simple** package. 


# Naming and Coding convention

## Naming

## Coding

### Style

### Packages

Wherever possible, base R functions should be used and chosen over functions from other packages. E.g., use

```{r, eval = FALSE}
dat2 <- 
  dat[
    dat$column == 1,
    ]
```

instead of

```{r, eval = FALSE}
library(dplyr)
dat2 <- 
  dat %>% 
  filter(
    column == 1
  )
```


# Misc

## Rationales

### Put patient baseline data in common data frame, but since outcomes might differ, put ISA specific outcomes in separate data frame for each ISA

## Vanilla assumptions for simplicity:

### Initial lIntrDsgn List object contains list of ISAs to be added throughout platform trial
 i.e. there is no waiting list, no ISAs enter of leave the candidate list, etc. 
 Later: Model ISA waiting list separately 

### ISAs open, then run, and then close. No re-opening.

### Between ISA allocation ratio is stored in the treatment dataset in a separate column

### List of snapshots is always created (especially when running OC function, this should be optional or off by default)

### Randomization is strictly two-stage

### All patients are eligible for all ISAs and Arms

### No drift in patient baseline parameters

### Patients arrive in blocks (per week) -> sample sizes not exactly reachable
